IPv6 over Low-Power Wireless Personal Area Networks\\ MSc. Thesis Proposal

### 2009-12-16 trunk/doc/msc-proposal/msc-proposal.tex
proposal: added structure

%%
%	Transmission of IPv6 Packets
%%
\chapter{6LoWPAN Networks}\label{ch:6lowpan}
A low-power wireless personal area network (LoWPAN) is a simple low throughput wireless network comprising low cost and low power devices that conform to the IEEE 802.15.4-2003 standard. The IEEE 802.15.4-2003 standard specifies node-to-node frame delivery between the devices which are within reachable distance from each other. On top of IEEE 802.15.4 a network layer (layer 3 of the seven-layer OSI model) has to be defined that would provide end-to-end packet delivery including routing through intermediate hosts.

@@

\chapter{Neighbor Discovery Protocol}\label{ch:nd}
The Neighbor Discovery (ND) protocol for IPv6 \cite{rfc4861} provides for basic bootstrapping and network operation. Nodes (hosts and routers) use ND to determine the link-layer addresses for neighbors known to reside on attached links. Hosts also use ND to find neighboring routers that are willing to forward packets. In the previous Chapter \ref{ch:6lowpan} a mechanism which allows to carry IPv6 packets over IEEE 802.15.4 networks with the help of an adaptation layer has been described. However, the standard IPv6 Neighbor Discovery has several problems when using it with 6LoWPANs. IPv6 ND heavily uses multicast capabilities, whereas it is very expensive and not desirable in a low-power, lossy wireless network. Therefore, the classic ND is not suitable for 6LoWPANs. The Internet Draft \cite{draft-nd-07} specifies a Neighbor Discovery mechanism optimized for LoWPAN networks. This chapter describes the 6LoWPAN ND protocol.

\section{Overview}\label{Overview}
6LoWPAN Neighbor Discovery (6LoWPAN-ND) provides an optimized neighbor discovery mechanism sufficient for LoWPAN operation. 6LoWPAN-ND introduces a node registration mechanism optimizing the node-router interface.  This mechanism requires no flooding and reduces link-local multicast frequency. Nodes in the LoWPAN register with Routers and Edge Routers (IPv6 routers that interconnect the LoWPAN to another IP network), creating state about nodes attached to that router (binding table) and about all IPv6 addresses in the LoWPAN. This state information is stored within a conceptual data structure, Whiteboard, located at Edge Routers (ERs). The Whiteboard makes use of soft bindings that contain an Owner Interface Identifier, Owner Nonce, IPv6 address and a remaining lifetime of the binding. Nodes send periodic registration messages in order to maintain their bindings. The detection of duplicate addresses (DAD) is performed across the entire LoWPAN using a lookup on the Whiteboard using the node registration mechanism.

6LoWPAN-ND makes use of Router Solicitation (RS) / Router Advertisement (RA) message exchanges similar to classic ND. In 6LoWPAN-ND RA messages may carry additional options for context dissemination and are reduced in size. In addition to RS and RA messages, 6LoWPAN-ND defines two new ICMP packet types: Node Registration (NR), which is sent by a node to an Edge Router to register a binding for an IPv6 address in the Whiteboard, and Node Confirmation (NC) by which an Edge Router replies to the registering node.

%%
%	Conclusion
%%
\chapter*{Proposed work}
\addcontentsline{toc}{chapter}{Proposed work}

>>>>

%%
%	Transmission of IPv6 Packets
%%
\chapter{Transmission of IPv6 Packets over IEEE 802.15.4}\label{ch:6lowpan}
A low-power wireless personal area network (LoWPAN) is a simple low throughput wireless network comprising low cost and low power devices that conform to the IEEE 802.15.4-2003 standard. The IEEE 802.15.4-2003 standard specifies node-to-node frame delivery between the devices which are within reachable distance from each other. On top of IEEE 802.15.4 a network layer (layer 3 of the seven-layer OSI model) has to be defined that would provide end-to-end packet delivery including routing through intermediate hosts.

@@

\input{msc-routing}

\input{msc-nd}
%%
%	Conclusion
%%
\chapter*{Proposed work}
\addcontentsline{toc}{chapter}{Proposed work}
